Radio Emission from Red-Giant Hot Jupiters

### 2015-12-22 reply2referee.txt

  We now resubmit our paper titled "Radio Emission from Red Giant Hot
Jupiters" by Yuka Fujii and collaborators, having addressed the
referee's points.  In so doing we have provided additional explanatory
text and updated the references, both in ways suggested by the referee
and on our own initiative.  Below is our point-by-point response to
the referee.  In our response, we present the referee's comments
preceded by "## ", and our own comments indented in the space that
follows.  We have also revised the reference list to match the
journal's nomenclature.

  We realized upon reading the referee's report that we should have
done a better job of motivating some of the sections in our paper.
For instance, we wrote the section about the "canceling field"
generated by stellar-wind electrons, as they spiral down field lines
in accreting onto the planet, in order to allay the reader's possible
concerns that the planetary magnetic field would be significantly
attenuated by the canceling field that would be generated by the
massive stellar wind from an AGB star -- a possibility that we
wrestled with for probably 100 hours.  We hope to save our readers
from having to repeat the same thought process we went through by
laying out the logic clearly.  However, it seems that we didn't
explain well enough why we put this section in the paper; in this
resubmission, we have tried to better motivate the parts that the
referee thought were less germane.

  In addition, it appears that the referee and we have somewhat
different philosophies regarding the purpose of a paper.  For example,
the referee suggests that we eliminate the section "Assumptions for
planetary magnetic field" and instead simply state that we assume a
magnetic field of 10G.  In our view, this would significantly weaken
our manuscipt.  Our aim is not merely to explain the assumptions that
go into making each figure and table but also to walk the reader
through the physics of the processes under discussion.

  Finally, we point out that this comment from the report was
surprising:
----
  "Section 2.5 This section is new, but not necessary, as Ignace
   (2010) have already addressed the issue of the ionisation of the
   exoplanetary exosphere."
----
Ignace considered ionization purely due to shock heating as the stellar
wind flows past the exoplanet.  The physical picture we propose is 
different, namely that significant ionization can occur as wind material
is accreted onto the exoplanets surface.  We quantify this result as a
function of distance from the planet and planetary mass while 
considering the effect of secondary ionization by ionized electrons.  
These results suggest substantial ionization to large radii.  As the 
referee states that this section is new and as we can find no evidence
of this scenario in Ignace 2010, we prefer to keep this section in the 
manuscript.

[YF: I added the section above to include Jason's feedback. Will we 
remove the following part instead?]
Our manuscript presents a more detailed and accurate description of
the ionization profile around a planet accreting stellar wind than
that in Ignace et al.'s paper.  It is unusual, in our experience, for
a referee to say that a description that is new, correct, and more
detailed than another description in the literature, is unnecessary.

### 2015-12-22 reply2referee.txt

                                                22 December 2015

Dear Dr. Burton,

  We now resubmit our paper titled "Radio Emission from Red Giant Hot
Jupiters" by Yuka Fujii and collaborators, having addressed the
referee's points.  In so doing we have provided additional explanatory
text and updated the references, both in ways suggested by the referee
and on our own initiative.  Below is our point-by-point response to
the referee.  In our response, we present the referee's comments
preceded by "## ", and our own comments indented in the space that
follows.  We have also revised the reference list to match the
journal's nomenclature.

  We were surprised to see that the referee's report suggests
that our manuscript is an "amendment to the Ignace (2010) result" and
that the manuscript's length could be reduced by a factor of four.
Much of what the referee thinks is not new or original is either
entirely new or pulls literature results together in new ways.  In
this prefatory note to you, we'd like to point out a few examples of
parts that the referee thought should be cut where we think the
referee's judgment is misguided.

  For instance, this comment from the report was surprising:
----
  "Section 2.5 This section is new, but not necessary, as Ignace
   (2010) have already addressed the issue of the ionisation of the
   exoplanetary exosphere."
----
Ignace considered ionization purely due to shock heating as the
stellar wind flows past the exoplanet.  The physical picture we
propose is different, namely that significant ionization can occur as
wind material is accreted onto the exoplanets surface.  We quantify
this result as a function of distance from the planet and planetary
mass while considering the effect of secondary ionization by ionized
electrons.  These results suggest substantial ionization to large
radii.  Since the referee states that this section is new and as we
can find no evidence of this scenario in Ignace (2010), we prefer to
keep this section in the manuscript.  We note that it is unusual, in
our experience, for a referee to say that a description that is new,
correct, and more detailed than another description in the literature,
is unnecessary.

  Another example is the referee's comment about the section on radio
observability: "Much of this section could be cut, saving perhaps
section 4.2. Predictions for observations with different facilities
have been made many times before."  We strongly disagree with the
referee's judgment here; in fact, the section on radio observability
could have been a separate short paper on its own.  Our reply to the
referee below addresses this point, but we here hope to underscore
that we believe there is no paper in the literature where one can find
predictions for the observability of this class of object with
state-of-the-art facilities in 2015-2016 and beyond; certainly, if
such predictions exist in the literature, the referee did not point
out where.

  The referee's report did help us to realize where we could have done
a better job motivating some of the sections in our paper.  For
instance, we wrote the section about the "canceling field" generated
by stellar-wind electrons, as they spiral down field lines in
accreting onto the planet, in order to allay the reader's possible
concerns that the planetary magnetic field would be significantly
attenuated by the canceling field that would be generated by the
massive stellar wind from an AGB star -- a possibility that we
wrestled with for probably 100 hours.  We hope to save our readers
from having to repeat the same thought process we went through by
laying out the logic clearly.  However, it seems that we didn't
explain well enough why we put this section in the paper; in this
resubmission, we have tried to better motivate the parts that the
referee thought were less germane.

  Finally, it appears that the referee and we have somewhat different
philosophies regarding the purpose of a paper.  For example, the
referee suggests that we eliminate the section "Assumptions for
planetary magnetic field" and instead simply state that we assume a
magnetic field of 10G.  In our view, this would significantly weaken
our manuscipt.  Our aim is not merely to explain the assumptions that
go into making each figure and table but also to walk the reader
through the physics of the processes under discussion.

### 2015-12-24 ms.tex
including Neil's comment

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage{color,xcolor}
\usepackage{url}
\usepackage{ulem}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
\allowdisplaybreaks[1]

\bibliographystyle{apj}

\definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}
\def\memoTM#1{\color{DarkGreen}${\bf #1}$ \color{black}}

@@

@@

\revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
%While interacting with magnetic field, the ionized portion could lose their energy 
%Therefore, some part of the incoming wind particles are what we could envision is the 
%Considering other uncertainties of radio wave generation, we 
The detailed electromagnetic structure around RGHJs therefore requires  elaborate numerical simulations, which is beyond the scope of this paper. Noting that all other uncertainties, in this paper we simply aim at giving an order-of-magnitude estimate. }

@@

In order to examine the realistic potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions. 
For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
\revise{}{We note that these data do not unambiguously distinguish RG from early AGB stars and thus the list likely includes about 40\% of early AGB stars. }
For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
%%%
\begin{equation}
\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
\end{equation}
%%%
where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$ is the stellar luminosity, $\tilde R = R_{\star }/R_{\odot }$ is the stellar radius, $\tilde M = M_{\star }/M_{\odot }$ is the stellar mass, and $g$ is the surface gravity. 
The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
%%%
\begin{equation}
v \sim \sqrt{\frac{2GM_\star}{4R_{\star }}}
\end{equation}
%%%
The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
%%%
\begin{equation}
t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
\end{equation}
%%%
Combining this relation with equations (\ref{eq:fcyc}) and (\ref{eq:scalingB}) results in
%%%
\begin{equation}
\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} 
\end{equation}
%%%
In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.

@@

\revise{}{A more realistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
Observations of main-sequence stars implies that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
Assuming the same population for RG systems, the expected number of actual detection from RGHJs would be order of unity.  
A more detailed examination using the empirical planet mass function by \citet{cumming2008} is given in Appendix \ref{s:expectedvalue}. 
The analysis indicates that if the detection limit is 10$\mu {\rm Jy}$ the total expected value is about 3. }
%However, as we see in the next subsection, the . and the expected value for massive planets ($M_p>5M_{\rm J}$) which supposedly have relatively high cyclotron frequency is about 1-2.

@@

\revise{%
Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.%
}{%
Once planetary radio emission is detected, it in general provides a unique approach for learning the planetary property. As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites. If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g. radial-velocity observations, tests  the proposed scaling law of planetary dynamo. 
A extra fruit from observations of RGHJs in particular is that the lower cut-off frequency, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit. In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''. %
We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars. %
}

@@

The conventional escape parameter is computed for RGHJs as follows
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\lambda _c = \frac{G M_p m_{\rm p}}{k T_c r_c} = 218 \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{T_c}{1000 {\rm K}} \right)^{-1} \left( \frac{r_c}{R_{\rm J}} \right)^{-1}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $T_c$ and $r_c$ are the radius and temperature at exobase. In most of the cases we consider, therefore, the escape is safely assumed to be Jeans escape. 
The rate of Jeans escape is 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{equation}
%\dot M = 4 \pi \rho_0 a r^2 \left( \frac{v_{\rm esc}(r_0)}{2a} \right)^2 \exp \left( - \frac{v_{\rm esc}^2 (r_0) }{2 a^2} + \frac{3}{2} \right)
%\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{eqnarray}
%\Phi _{\rm Jeans} &=& 4 \pi r_c^2 \cdot \frac{n_c}{2 \sqrt{\pi}} B \sqrt{\frac{2 k_B T_c }{m}} ( 1 + \lambda _c ) e^{-\lambda _c} \\
\Phi _{\rm Jeans} (r_c) &=& \frac{1}{\sigma } \sqrt{ \frac{G M_p}{2 R_p^3} } \left( \lambda _c + 1 \right) \sqrt{ \lambda _c } e^{-\lambda _c} \\
%&=& 1/(pi*(0.529e-10)**2)*sqrt(2*6.674e-11*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) 
%&=& 1/(pi*(0.529)**2)*sqrt(2*66.74*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) * 1e14
\end{eqnarray}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $\sigma $ is the cross section of hydrogen atoms, assumed to be equal to Bohr radius here [[OK??]]. 
The ram pressure at distance $r$ due to such an outflow is
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{eqnarray}
P_{\rm ram} (r) &=& m_{\rm p} \Phi _{\rm Jeans} (r_c) \left( \frac{r}{R_p} \right)^{-2} v_{\rm esc} 
% 1.674e-27 * 5.3e18 / 100.0 * 59.5e3 
%&=& 5.27 \times 10^{-6} ~{\rm Pa} \; \left( \frac{r}{10~R_p} \right)^{-2} \left( \frac{M_p}{M_{\rm J}} \right)^{1/2}
\end{eqnarray}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
which indicates $3.6\times 10^{-7}~{\rm barye}$ even when $\lambda _c = 1$. 
On the other hand, the ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim 2.7 \times 10^{-5} ~{\rm barye}$. 
This implies that the ram pressure of the planetary outflow would be negligible.

>>>>

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage{color,xcolor}
\usepackage{url}
\usepackage{ulem}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
\allowdisplaybreaks[1]
\bibliographystyle{apj}

\definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}

@@

%%%%%%% this part is to be removed eventually %%%%%%%
\def\memoTM#1{\color{DarkGreen}${\bf #1}$ \color{black}}
\def\memoYF#1{\color{red}$\leftarrow${\bf #1} \color{black}}

@@

\revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
%While interacting with magnetic field, the ionized portion could lose their energy 
%Therefore, some part of the incoming wind particles are what we could envision is the 
%Considering other uncertainties of radio wave generation, we 
The detailed electromagnetic structure around RGHJs therefore requires  elaborate numerical simulations, which is beyond the scope of this paper. Noting these uncertainties, in this paper we simply aim to give an order-of-magnitude estimate. }

@@

In order to examine the realistic potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions. 
For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
\revise{}{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list likely consists of about 40\% early AGB stars. }\memoYF{Doesn't ``consists of'' sound like ``A is made of B''?}
For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
%%%
\begin{equation}
\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
\end{equation}
%%%
where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$ is the stellar luminosity, $\tilde R = R_{\star }/R_{\odot }$ is the stellar radius, $\tilde M = M_{\star }/M_{\odot }$ is the stellar mass, and $g$ is the surface gravity. 
The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
%%%
\begin{equation}
v \sim \sqrt{\frac{2GM_\star}{4R_{\star }}}
\end{equation}
%%%
The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
%%%
\begin{equation}
t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
\end{equation}
%%%
Combining this relation with equations (\ref{eq:fcyc}) and (\ref{eq:scalingB}) results in
%%%
\begin{equation}
\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} 
\end{equation}
%%%
In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.

@@

\revise{}{A more realistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
Observations of main-sequence stars imply that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
Assuming the same population for RG systems, the expected number of actual detection from RGHJs would be of order unity.  
A more detailed examination using the empirical planet mass function by \citet{cumming2008} is given in Appendix \ref{s:expectedvalue}. 
The analysis indicates that if the detection limit is 10$\mu {\rm Jy}$ the total expected value is about 3. }
%However, as we see in the next subsection, the . and the expected value for massive planets ($M_p>5M_{\rm J}$) which supposedly have relatively high cyclotron frequency is about 1-2.

@@

\revise{%
Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.%
}{%
Once planetary radio emission is detected, it in general provides a unique approach for learning the planetary property. As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites. If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g. radial-velocity observations, tests  the proposed scaling law of planetary dynamo. 
Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit. In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''. %
We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars. %
}

@@

The conventional escape parameter is computed for RGHJs as follows
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\lambda _c = \frac{G M_p m_{\rm p}}{k T_c r_c} = 218 \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{T_c}{1000 {\rm K}} \right)^{-1} \left( \frac{r_c}{R_{\rm J}} \right)^{-1}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $T_c$ and $r_c$ are the radius and temperature at exobase. In most of the cases we consider, therefore, the escape is safely assumed to be Jeans escape. 
The rate of Jeans escape is 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{equation}
%\dot M = 4 \pi \rho_0 a r^2 \left( \frac{v_{\rm esc}(r_0)}{2a} \right)^2 \exp \left( - \frac{v_{\rm esc}^2 (r_0) }{2 a^2} + \frac{3}{2} \right)
%\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{eqnarray}
%\Phi _{\rm Jeans} &=& 4 \pi r_c^2 \cdot \frac{n_c}{2 \sqrt{\pi}} B \sqrt{\frac{2 k_B T_c }{m}} ( 1 + \lambda _c ) e^{-\lambda _c} \\
\Phi _{\rm Jeans} (r_c) &=& \frac{1}{\sigma } \sqrt{ \frac{G M_p}{2 R_p^3} } \left( \lambda _c + 1 \right) \sqrt{ \lambda _c } e^{-\lambda _c} \\
%&=& 1/(pi*(0.529e-10)**2)*sqrt(2*6.674e-11*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) 
%&=& 1/(pi*(0.529)**2)*sqrt(2*66.74*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) * 1e14
\end{eqnarray}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $\sigma $ is the cross section of hydrogen atoms, assumed to be equal to Bohr radius here \memoYF{OK??}. 
The ram pressure at distance $r$ due to such an outflow is
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{eqnarray}
P_{\rm ram} (r) &=& m_{\rm p} \Phi _{\rm Jeans} (r_c) \left( \frac{r}{R_p} \right)^{-2} v_{\rm esc} 
% 1.674e-27 * 5.3e18 / 100.0 * 59.5e3 
%&=& 5.27 \times 10^{-6} ~{\rm Pa} \; \left( \frac{r}{10~R_p} \right)^{-2} \left( \frac{M_p}{M_{\rm J}} \right)^{1/2}
\end{eqnarray}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
which indicates $3.6\times 10^{-7}~{\rm barye}$ even when $\lambda _c = 1$. 
On the other hand, the ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim 2.7 \times 10^{-5} ~{\rm barye}$. 
This implies that the ram pressure of the planetary outflow would be negligible.
